### 2021-07-09 rad-icfp-2021/generalization.tex
.
minor

\begin{small}
\begin{tabular}{|r c l|}
\hline
$\directD{\rho}{\Gamma}{Y}$(!reduce (x,y.e1) e$_2$ e$_3$!) 
&=& $\ldots$ same as Figure~\ref{fig:direct_diff_macro} up until !A_$3$! \\
&& !let B$_0$=map2 (a,b ->(!$\grad_\Gamma$!e)[a/x,b/y] A$_0$ A) in!\\
&& !let B$_1$=scanr $1_\Gamma$ $\widehat{\times}$ B$_0$ in! \\
&& !let B$_2$=reduce $\widehat{+}$ $0_\Gamma$ B$_1$ in! \\
&& !<reduce (x,y.e1) y$_1$ A, fun (x$_1$,$\ldots$,x$_n$,z) ->! \\
&& !Y((x$_1$,$\ldots$,x$_n$)$\widehat{+}(z*$B$_2$),0,map2 (a,b. a*b*z) A$_2$ A$_3$)! \\ \hline
\end{tabular}
\end{small}
\caption{The reverse-mode AD transformation of \codekw{reduce} without restrictions on its function argument.}
\label{fig:lift_reduce}
\end{figure}

@@

\begin{tabular}{r c l}
    $\directD{\rho}{\Gamma}{Y}$(!if e$_1$ then e$_2$ else e$_3$!) 
    &=& !let b=e$_1$ in!   \\
    && !<if b then e$_2$ else e$_3$, fun (x$_1$,$\ldots$,x$_n$,z) ->! \\
    && !Y(b*!$\directD{\rho}{\Gamma}{Y}$!(e$_2$)(x$_1$,$\ldots$,x$_n$,z)+!\\
    && \quad!(1-b)*!$\directD{\rho}{\Gamma}{Y}$!(e$_3$)(x$_1$,$\ldots$,x$_n$,z))>!
\end{tabular}

@@

\begin{tabular}{r c l}
    $\directD{\rho}{\Gamma}{Y}$(!if e$_1$ then e$_2$ else e$_3$!) 
    &=& !let b=e$_1$ in!   \\
    && !<if b then e$_2$ else e$_3$, fun (x$_1$,$\ldots$,x$_n$,z) ->! \\
    && !Y((x$_1$,$\ldots$,x$_n$)!$\widehat{+}$($\grad_\Gamma$!(e$_2$)*b!$\widehat{+}\grad_\Gamma$!(e$_3$)*(1-b))*z)>!\\
\end{tabular}

>>>>

\begin{small}
\begin{tabular}{|r c l|}
\hline
$\directD{\rho}{\Gamma}{Y}$(!reduce (x,y.e1) e$_2$ e$_3$!) 
&=& $\ldots$ same as Figure~\ref{fig:direct_diff_macro} up until !A_$3$! \\
&& !let B$_0$=map2 (a,b ->(!$\grad_\Gamma$!e)[a/x,b/y] A$_0$ A) in!\\
&& !let B$_1$=scanr $1_\Gamma$ $\widehat{\times}$ B$_0$ in! \\
&& !let B$_2$=reduce $\widehat{+}$ $0_\Gamma$ B$_1$ in! \\
&& !<reduce (x,y.e1) y$_1$ A, fun (x$_1$,$\ldots$,x$_n$,z) ->! \\
&& !Y((x$_1$,$\ldots$,x$_n$)$\widehat{+}(z*$B$_2$),0,map2 (a,b. a*b*z) A$_2$ A$_3$)! \\ \hline
\end{tabular}
\end{small}
\vspace{-0.4cm}
\caption{The reverse-mode AD transformation of \codekw{reduce} without restrictions on its function argument.}
\vspace{-0.4cm}
\label{fig:lift_reduce}
\end{figure}

@@

\begin{tabular}{l}
    $\directD{\rho}{\Gamma}{Y}$(!if e$_1$ then e$_2$ else e$_3$!) \\
    !let b=e$_1$ in <if b then e$_2$ else e$_3$, fun (x$_1$,$\ldots$,x$_n$,z) ->! \\
    !Y(b*!$\directD{\rho}{\Gamma}{Y}$!(e$_2$)(x$_1$,$\ldots$,x$_n$,z)+(1-b)*!$\directD{\rho}{\Gamma}{Y}$!(e$_3$)(x$_1$,$\ldots$,x$_n$,z))>!
\end{tabular}

@@

\begin{tabular}{l}
    !$\directD{\rho}{\Gamma}{Y}$(if e$_1$ then e$_2$ else e$_3$) = let b=e$_1$ in <if b then e$_2$ else e$_3$,! \\
    !fun (x$_1$,$\ldots$,x$_n$,z) -> Y((x$_1$,$\ldots$,x$_n$)!$\widehat{+}$($\grad_\Gamma$!(e$_2$)*b!$\widehat{+}\grad_\Gamma$!(e$_3$)*(1-b))*z)>!\\
\end{tabular}
